Weak gravitational lensing shear estimates with \textsc{metacalibration} for the \emph{Roman} High-Latitude Imaging Survey

### 2021-11-18 roman_metacal_v2.tex
v1 to v2

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\normalem
\title[Metacalibration with Roman High-Latitude Imaging Survey]{Weak gravitational lensing shear estimates with \textsc{metacalibration} for the High-Latitude Imaging Survey Program of the \emph{Roman} Space Telescope}

@@

% Abstract of the paper
\begin{abstract}
We investigate the performance of the \textsc{metacalibration} in the framework of the \emph{Nancy Grace Roman} Space Telescope (\emph{Roman}) image simulations. Measuring shear bias is a conclusive way to confirm that the requirements of the instrument and the overall weak lensing survey strategy are met, and that none of the processes in image simulations biases the science with real data. The weak lensing program of \emph{Roman} mission requires the galaxy shapes to be calibrated within about 0.03\%. To reach this goal, we can test our calibration process with these simulations and can isolate the sources where these residual shear biases arise. We incorporate several new realistic processing-pipeline updates necessary to calibrate shear with a better precision relative to the previous version of the simulations. We found that compared with the non-calibrated results from the previous work, \textsc{metacalibration} can significantly reduce the shear calibration bias. With the single-epoch images, across all three filters we are able to achieve the multiplicative bias, \textcolor{red}{$m=0.70\%$ within 1.8 $\sigma$ and additive bias, $c=3.37\times10^{-4}$ within xx $\sigma$}. $c$ is worse for the coadded images due to the strong correlation with the input PSF while \textcolor{red}{$m=-2.16\%$ for the multiband coadds}. In both single-epoch and coadd cases, we find that shape calibration becomes worse with decreasing image sampling factor. Overall, within the current simulation volume, \textsc{metacalibration} does not calibrate shapes with zero shear bias on relatively undersampled images that \emph{Roman} will produce. In the future, we will need to substantially increase the simulation volume to reach the accuracy necessary for the program. 
\end{abstract}

@@

Since the formulation of the physical cosmological model, more observational evidence has shown that the contents of the universe are mostly in the dark sector (\citealt{2020A&A...633A..69H, 2018PhRvD..98d3528T, 2019PhRvL.122q1301A, 2019PASJ...71...43H, 2021A&A...645A.104A}). Within the sector, dark energy accounts for the accelerating expansion of the universe (e.g., \citealt{1998AJ....116.1009R, 1999AIPC..478..129P}) and the combination of dark energy and dark matter which only interacts with non-relativistic matter are responsible for the growth of the large-scale structure (\citealt{2015RPPh...78h6901K, 2017grle.book.....D}). The growth can be studied by carefully reconstructing the paths of the light leaving distant galaxies and going through the region where masses concentrate in the universe; this physical phenomenon is called gravitational lensing. “Weak” gravitational lensing causes a slight distortion to intrinsic galaxy shapes when observed from the Earth. By detecting millions of these gravitationally lensed galaxies and computing their distortion levels, we can explore the matter density and the amplitude of matter fluctuation in the universe (e.g., \citealt{2001PhR...340..291B}). Measuring these quantities eventually help us learn the history of the development of the large-scale structure in the universe. For that reason, weak lensing is and will continue to be one of the powerful probes in the current and next-decade imaging surveys to constrain cosmological parameters with high precision. \par

Due to the subtlety in the lensing effect and its systematics dominant nature in the “weak” regime, observational efforts have been challenging. Over the past decade, large international collaborations such as the Dark Energy Survey\footnote{\url{http://www.darkenergysurvey.org/}} (DES: \citealt{2005astro.ph.10346T}), the Hyper Supreme-Cam\footnote{\url{http://hsc.mtk.nao.ac.jp/ssp/}} (HSC: \citealt{2018PASJ...70S...4A}), and the Kilo-Degree Survey\footnote{\url{http://kids.strw.leidenuniv.nl/}} (KiDS) have been successful at constraining the cosmological parameters, and the precision in calibrating the shapes of distant galaxies has reached a few percent (\citealt{2020arXiv201103408G, 2020arXiv201208567M, 2021A&A...645A.105G}). As we cover more areas in the sky and develop better tools (observatories and algorithms), we find more galaxies and we have already reached to the point where statistical and systematic uncertainties are comparable. Thus, the next-decade legacy surveys, the Stage IV surveys (\citealt{2006astro.ph..9591A}) such as Euclid\footnote{\url{ http://sci.esa.int/euclid}} (Euclid Study Scientist \& the Science Advisory Team 2010), the Vera C. Rubin Observatory Legacy Survey of Space and Time\footnote{\url{ http://www.lsst.org}} (LSST: \citealt{2009arXiv0912.0201L, 2019ApJ...873..111I}), and \emph{Nancy Grace Roman} Space Telescope\footnote{\url{https://roman.gsfc.nasa.gov}} (\emph{Roman}: \citealt{2015arXiv150303757S}) require even better control of systematics. In order to manage the systematic uncertainties, we must develop realistic image simulations, apply the pre-existing shape measurement on the simulated images, and determine any potential systematic effects and build the strategy of mitigating them.

Based on our current knowledge, systematic biases for weak lensing science, both observational and astrophysical, could occur throughout imaging surveys (e.g., \citealt{2018ARA&A..56..393M}). Particularly, observational systematics can be found in, 
\begin{itemize}
    \item observing strategy
    \item instrumentation effects such as Brighter-Fatter Effect
    \item post-processing pipeline such as image coaddition and object detection
\end{itemize}

In this study, we focus on shear calibration bias, which describes the relationship between gravitational lensing shear and measured galaxy shapes. In the limit of weak lensing ($\lvert\gamma\rvert\ll1$), the ensemble average of ellipticities $\langle e \rangle$ of galaxy shapes is directly related to the shear field $\gamma$, and the estimated shear can be written as a linear model with multiplicative ($m_{i}$) and additive bias ($c_{i}$) as described in the equation below. (\citealt{2006MNRAS.368.1323H, 2006MNRAS.366..101H, 2007MNRAS.376...13M}) 
\begin{equation}
    \gamma^{obs}_{i} = (1+m_{i})\gamma^{true}_{i} + c_{i}, 
    \label{eqn:linear}
\end{equation}
where i=(1,2) and $\gamma^{obs}_{i}$ is the two-component observed shear after calibrations and $\gamma^{true}_{i}$ is the true shear. The bias arises for various reasons. For space-based surveys, the bias can be mainly introduced in places such as PSF modelling, blending, and the undersampling of the image (e.g., \citealt{2018ARA&A..56..393M}). Additionally, complex detector effects such as brighter-fatter effect are the potential sources of bias (\citealt{2013MNRAS.429..661M}), where it is shown that for \emph{Roman} the effect of persistence will not be an issue (\citealt{2021arXiv210610273L}). Qualitatively, if the recovered shear is biased by 1$\%$ (m=0.01), $S_{8} = \sigma_{8} \sqrt{\Omega_{m}/0.3}$ would be biased about 1.5$\%$ in the final cosmology result. Thus, quantifying these biases before the real survey is extremely important. \par

Several shear calibration and bias mitigation efforts have been proposed by STEP (\citealt{2006MNRAS.368.1323H, 2007MNRAS.376...13M}) and GREAT (\citealt{2010MNRAS.405.2044B, 2013ApJS..205...12K, 2015MNRAS.450.2963M}) challenges, to meet the requirements for the current imaging surveys. In particular, one of the state-of-the-art self-calibration methods, \textsc{metacalibration} (\citealt{2017arXiv170202600H, 2017ApJ...841...24S}) has been shown to be able to reduce the significant of shear bias. It has also confirmed that the shear can be calibrated with \textsc{metacalibration} at a-few-percent level in DES (\citealt{2018MNRAS.481.1149Z, 2020arXiv201103408G}), without accounting for galaxy blending. Tackling the issue of blending is on the way of DES Y6 analysis with the shear-dependent detection and calibration technique (\textsc{metadetect}; \citealt{2020ApJ...902..138S}). While the major advantage of \textsc{metacalibration} is that it can be directly applied upon real galaxy images, which does not depend on galaxy morphology in simulations, the limitations for future surveys are not well-known. One possible limitation might lie in the effect of the undersampled images, because future space-based surveys like \emph{Euclid} and \emph{Roman} have such a small pixel scale that galaxy images will not be Nyquist sampled at a native resolution (\citealt{2013PASP..125.1496S}) based on the Nyquist-Shannon Sampling Theorem. We define the sampling factor of each filter in \emph{Roman} to be, 
\begin{equation}
    Q = \frac{\lambda_{min}N_{f}}{p}, 
    \label{eqn:sampling}
\end{equation}
where $\lambda_{min}$ is the shortest wavelength of the incident light in the filter, $N_{f}$ is the focal ratio of the telescope ($N_{f}=7.8$ for \emph{Roman}) and $p$ is the pixel spacing of the sensor ($p=10\mu m$ for \emph{Roman}). The image with the sampling factor, $Q < 2$, is not Nyquist sampled and reffered to as the undersampled image. It is problematic to measure galaxy shapes solely from the undersampled images, because the \emph{Roman} PSF that will be used to recover the shapes is also undersampled and has a complex structure, not simply Gaussian. \textcolor{red}{It is, therefore, necessary to build a robust strategy that can reconstruct better sampled PSF to allow unbiased shape measurement. }

Recently, Kannawadi et al. (2021) addressed this potential issue of the limitations of \textsc{metacalibration} on undersampled images on \emph{Euclid} image simulations. They found that for \emph{Euclid} mission the shear estimate is biased about 1$\%$ (\citealt{2021MNRAS.502.4048K}). It is mentioned that their result could be extended to the \emph{Roman} mission due to their similarities in the instruments and for \emph{Roman} they predicted the multiplicative bias was more than 1\% for H158 and F184 filters. Regardless of this extended result, we should validate if \textsc{metacalibration} is unbiased with the image simulations specifically made for the \emph{Roman} mission. Our work is based on the image simulation suite of the \emph{Roman} Space Telescope developed by \citet{2021MNRAS.501.2044T}, where we render star and galaxy images from \texttt{GalSim}\footnote{\url{ https://github.com/GalSim-developers/GalSim}} (\citealt{2015A&C....10..121R}). With a few simulation updates and an implementation of \textsc{metacalibration}, we can start to explore if the shear calibration goal of the High-Latitude Survey program for \emph{Roman} ($m=~3.2\times10^{-4}$) (\citealt{2019BAAS...51c.341D}) can be achieved. \par

@@

\section{Simulations}
\label{sec:sims}
In this section, we briefly summarize the full simulation details from building a truth catalog to measuring galaxy shapes. Then we describe the simulation updates that are implemented for this work.
\subsection{Simulation Summary}
\label{subsec:imsim}
The base of our image simulations of the \emph{Roman} Space Telescope is the \emph{Roman} simulation suite\footnote{\url{ https://github.com/matroxel/roman_imsim}} developed by \citet{2021MNRAS.501.2044T}, which renders realistic galaxy and star images on 18 Sensor-Chip Assemblies (SCAs) of a 2.5$\times$2.5 deg$^{2}$ patch of the sky provided the observing strategy for the 5-year reference mission and Cycle7 specifications\footnote{\url{https://roman.gsfc.nasa.gov/science/Roman_Reference_Information.html}}. We begin by creating a truth catalog using the simulated galaxy distribution from the Buzzard simulation (\citealt{2019arXiv190102401D}), photometric galaxy catalog sampled from the CANDELS survey (e.g., \citealt{2019ApJ...877..117H}), and Milky Way simulation (Galaxia; \citealt{2011ApJ...730....3S}) for star positions and magnitudes. Then, the following properties are applied to each galaxy.
\begin{itemize}
    \item positions (RA, Dec)
    \item photometries for each \emph{Roman} filter (F184/H158/J129/Y106)
    \item intrinsic galaxy shapes and random orientations
    \item flux ratios of de Vaucouleurs bulge, exponential disk, and star-forming knots
    \item artificial gravitational lensing shears
\end{itemize} 
Within the identical realizations of the simulation, we produce four truth catalogs using four sets of gravitational shears ($e_{1}$, $e_{2}$)=\{(+0.02, 0.00), (-0.02, 0.00), (0.00, +0.02), (0.00, -0.02)\}. This approach helps us to reduce shape and measurement noise when taking the difference in recovered shapes to compute multiplicative bias (\citealt{2019A&A...621A...2P}).

The next step of the process is to create postage stamps and SCA images using \texttt{GalSim}. In this stage, Point-Spread Function (PSF) is convolved with the stamps. Here, the \emph{Roman} PSF is rendered using the \texttt{galsim.roman} module under \texttt{GalSim}, which has implemented \emph{Roman}-specific instrument properties such as the PSF and World Coordinate System (WCS). The module is able to estimate an object position on the sky in RA, Dec using the \emph{Roman} WCS and produce the \emph{Roman} PSF which, for example, correctly describes the diffraction spikes pattern made by the struts and camera in the pupil plane.

After we generate the object stamps across all the SCAs and pointings, we create Multi-Epoch Data Structure (MEDS) files in which each unique object dictionary contains information of all the exposures. These MEDS files are generated according to the Hierarchical Equal Area isoLatitude Pixelisation (HEALPix) of $n_{side}=512$. These MEDS files contain all objects that are located in the area of the sky partitioned according to a HEALPix of $n_{side}$=512. Once the objects are sorted in MEDS files, we pass these multiple exposures with the corresponding PSF to \texttt{ngmix}\footnote{\url{ https://github.com/esheldon/ngmix}} to fit the galaxy shapes with the Gaussian mixture fitting method (\citealt{2014MNRAS.444L..25S}). This shape measurement process produces shape catalogs from which the shear calibration bias can be calculated with \textsc{metacalibration}.

\begin{figure}
	\includegraphics[width=\columnwidth]{figure1.pdf}
	\vspace*{-3mm}
    \caption{The rotation of the Roman PSF produced from the \texttt{galsim.roman} module. Position angle (PA) which determines the rotation of the telescope is $0^{\circ}$ and $30^{\circ}$. The rotation of the PSF is particularly important when an object has multiple exposures and needs to be coadded. If each galaxy image is rotated but each PSF is not, the coadded PSF would have a particular pattern and its shape would not be averaged down. By correctly rotating the PSF that is convolved with galaxy images, the effect of the PSF on the recoverd galaxy shape will be less.}
    \label{fig:psfrot}
\end{figure}

\begin{figure*}
	\includegraphics[width=\textwidth]{figure2.pdf}
	\vspace*{-10mm}
    \caption{The top row shows the first entry of the single epoch images and its coadded image, single and coadded oversampled PSF for an object with low signal-to-noise ratio (S/N=9.69). The bottom row shows the same for an object with high signal-to-noise ratio (S/N=1552.97).}
    \label{fig:singlecoadd}
\end{figure*}

\subsection{Simulation Updates}
In order to accomplish science goals, and build and test the pipelines of weak lensing program in \emph{Roman}, we must keep updating the simulations to be more realistic. We have implemented and made updates to the following parts of the simulation framework to be able to measure unbiased shapes with \textsc{metacalibration}. 
\begin{itemize}
    \setlength\itemsep{1em}
    \item \textbf{Saturation Cuts}:
    We have implemented the pixel saturation of 100,000 electrons. This value is an approximate pixel saturation but in the next generation of the simulations we will use the true saturation from the flight candidate detectors.

    \item \textbf{Rotation of the \emph{Roman} PSF on the sky}:
    In the study by Troxel et al. (2021), the rotations of the \emph{Roman} PSF with respect to the telescope rotation were not engaged properly by \texttt{galsim.roman} module. Since a non-rotating PSF could trigger a preferred direction in the shapes when being deconvolved, we believe that this contributed to the non-zero multiplicative bias result. There has been an update in \texttt{galsim.roman} module to correctly rotate the PSF given the WCS on the SCA. Figure \ref{fig:psfrot} shows a toy PSF of the same pointing but with a different rotation angle of the telescope.

    \item \textbf{Single-band and Multiband Coadds}: 
    We have added and modified the postage stamp coadds (\texttt{psc}) algorithm\footnote{\url{https://github.com/esheldon/psc}} to create coadditions of single-epoch postage stamps. Coadds are usually performed to enhance the signal-to-noise ratio (S/N) of an object and mitigate the measurement noise. If we take advantage of fitting an object in the coadd instead of fitting multiple images of each object in each filter, we can save a factor of 6 in computing time, which is the average number of exposures from the reference survey. Additionally, coadding is one way to reduce the effect of the undersampling of the images since the coadd is naturally better sampled. For these reasons, we must utilize a coadding scheme for the \emph{Roman} galaxies. The detailed overview of the coadd process in \texttt{psc} is in Sec. \ref{subsec:psc}.

    \item \textbf{\textsc{metacalibration} in \texttt{ngmix}}: We implemented \textsc{metacalibration}\footnote{\url{https://github.com/esheldon/ngmix/wiki/Metacalibration}} bootstrapper method, which is a wrapper class to run measurements in the \texttt{ngmix} package and is used extensively to produce weak lensing shape catalog in DES Y3 analysis. \textsc{metacalibration} process takes place after making coadded images. \texttt{ngmix} is able to fit multiple exposures in case for measuring shapes on single-epoch images. With this calibration method, we hope to significantly reduce some of the shear calibration bias Troxel et al. (2021) measured. The detailed overview of \textsc{metacalibration} can be found in Sec.\ref{subsec:mcal}. 
    %\item (Any other changes?)
\end{itemize}

@@

\section{Post-catalog Processes}
\label{sec:methods}
Our goal is to show that the recovered shapes with \textsc{metacalibration} are non-biased. In order to do so, we need to build a measurement pipeline within the current simulation framework that contributes to the final measurement. In this section, we present in detail how coadds are produced with \texttt{psc} from the undersampled single-epoch images, how \textsc{metacalibration} calibrates shapes, and how we measure the shear calibration bias from the \textsc{metacalibration} catalog.

>>>>

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\normalem
\title[Metacalibration with The Roman High-Latitude Imaging Survey]{Weak gravitational lensing shear estimates with \textsc{metacalibration} for the \emph{Roman} High-Latitude Imaging Survey}

@@

% Abstract of the paper
\begin{abstract}
We investigate the performance of the \textsc{metacalibration} shear calibration framework using image simulations for the \emph{Nancy Grace Roman} Space Telescope (\emph{Roman}) reference High-Latitude Imaging Survey (HLIS). These large-scale realistic image simulations are necessary to measure shear bias to confirm that the requirements of the instrument and the overall weak lensing survey strategy are met. The weak lensing program of the \emph{Roman} mission requires the galaxy shapes to be calibrated within about 0.03\%. To reach this goal, we can test our calibration process with these simulations and ultimately isolate the sources where these residual shear biases arise. In this work, we incorporate several new realistic processing-pipeline updates necessary to calibrate shear with a better precision relative to the previous version of the simulations and show first results for the reference HLIS using \textsc{metacalibration}. We find that compared with the non-calibrated results from previous work, \textsc{metacalibration} as used in current experiments can significantly reduce the shear calibration bias to the percent level. With the single-epoch images, across all three filters we are able to achieve a multiplicative bias \textcolor{red}{$m=0.70\%$ within 1.8 $\sigma$}, while for coadd cutouts, \textcolor{red}{$m=-2.16\%$}. In both single-epoch and coadd cases, we find that shape calibration becomes worse with decreasing image sampling factor. Overall, within the current simulation volume, there is evidence that \textsc{metacalibration} as currently implemented will not calibrate shapes with zero shear bias in the \emph{Roman} HLIS and further work on the shear calibration methodology is necessary. In the future, we will need to substantially increase the simulation volume to reach the precision necessary for the HLIS. \textcolor{red}{insert approx. factor of sim size needed}
\end{abstract}

@@

Since the formulation of a physical cosmological model, more observational evidence has shown that the contents of the universe are mostly in the dark sector (\citealt{2020A&A...633A..69H, 2018PhRvD..98d3528T, 2019PhRvL.122q1301A, 2019PASJ...71...43H, 2021A&A...645A.104A}). Within this sector, dark energy accounts for the accelerating expansion of the universe (e.g., \citealt{1998AJ....116.1009R, 1999AIPC..478..129P}) and the combination of dark energy and dark matter are responsible for the observed growth of large-scale structure (\citealt{2015RPPh...78h6901K, 2017grle.book.....D}). The growth can be studied by carefully reconstructing the paths of the light leaving distant galaxies and going through the regions where mass concentrates in the universe; this physical phenomenon is called gravitational lensing. “Weak” gravitational lensing causes a slight distortion to intrinsic galaxy shapes when observed from the Earth. By detecting millions of these gravitationally lensed galaxies and computing their ensemble distortion levels, we can explore the dark matter density and the amplitude of matter fluctuation in the universe (e.g., \citealt{2001PhR...340..291B}). Measuring these quantities eventually helps us learn about the history of the development of the large-scale structure in the universe. For that reason, weak lensing is one of the most powerful probes in current and near-future imaging surveys to constrain cosmological parameters with high precision. \par

Due to the subtlety in the lensing effect and its systematics-dominant nature in the weak regime, observational efforts have been challenging. Over the past decade, large international collaborations such as the Dark Energy Survey\footnote{\url{http://www.darkenergysurvey.org/}} (DES: \citealt{2005astro.ph.10346T}), the Hyper Supreme-Cam\footnote{\url{http://hsc.mtk.nao.ac.jp/ssp/}} (HSC: \citealt{2018PASJ...70S...4A}), and the Kilo-Degree Survey\footnote{\url{http://kids.strw.leidenuniv.nl/}} (KiDS)\textcolor{red}{insert cite like others} have been successful at constraining the cosmological parameters, and the precision in calibrating the shapes of distant galaxies has reached a few percent (\citealt{2020arXiv201103408G, 2020arXiv201208567M, 2021A&A...645A.105G}). As we observe more area of the sky and develop better tools (observatories and algorithms), we detect more galaxies, and have already reached the point where statistical and systematic uncertainties are comparable. Thus, near-future Stage IV surveys (\citealt{2006astro.ph..9591A}) such as Euclid\footnote{\url{ http://sci.esa.int/euclid}} (Euclid Study Scientist \& the Science Advisory Team 2010), the Vera C. Rubin Observatory Legacy Survey of Space and Time\footnote{\url{ http://www.lsst.org}} (\emph{Rubin}: \citealt{2009arXiv0912.0201L, 2019ApJ...873..111I}), and \emph{Nancy Grace Roman} Space Telescope\footnote{\url{https://roman.gsfc.nasa.gov}} (\emph{Roman}: \citealt{2015arXiv150303757S}) require even better control of systematics. In order to understand the systematic uncertainties we face, we must develop realistic image simulations, apply pre-existing shape measurement to the simulated images, and determine any potential residual systematic effects and build a strategy for modifying the calibration methodology to mitigate them.

Based on our current knowledge, systematic biases for weak lensing science, both observational and astrophysical, can occur at all stages of the imaging survey (e.g., \citealt{2018ARA&A..56..393M}). Particularly, observational systematics can be due to: 
\begin{itemize}
    \item inhomogeneous observing strategy,
    \item instrumentation effects,
    \item post-processing pipelines such as image coaddition and object detection.
\end{itemize}

In this study, we focus on the shear calibration bias, which describes the relationship between gravitational lensing shear $\gamma$ and measured galaxy shapes. In the limit of weak lensing ($\lvert\gamma\rvert\ll1$) and random intrinsic galaxy shapes, the ensemble average of ellipticities $\langle e \rangle$ of galaxy shapes is directly related to the shear field $\gamma$, and the estimated shear can be written as a linear model with multiplicative ($m_{i}$) and additive bias ($c_{i}$) as described in the equation below (\citealt{2006MNRAS.368.1323H, 2006MNRAS.366..101H, 2007MNRAS.376...13M}) 
\begin{equation}
    \gamma^{obs}_{i} = (1+m_{i})\gamma^{true}_{i} + c_{i}, 
    \label{eqn:linear}
\end{equation}
where i=(1,2) and $\gamma^{obs}_{i}$ is the two-component observed shear after calibrations and $\gamma^{true}_{i}$ is the true shear. The bias can be introduced in places such as PSF modeling, blending, and the undersampling of the image (e.g., \citealt{2018ARA&A..56..393M}). Additionally, complex detector effects such as the brighter-fatter effect are potential sources of bias (\citealt{2013MNRAS.429..661M}), while it has been shown that for \emph{Roman} the effect of persistence will not be an issue (\citealt{2021arXiv210610273L}). Qualitatively, if the recovered shear is biased by 1$\%$ (m=0.01), $S_{8} = \sigma_{8} \sqrt{\Omega_{m}/0.3}$ could be biased about 1.5$\%$ in the final cosmology result. Thus, quantifying and correcting these biases before the real survey begins is extremely important. \par

Several shear calibration and bias mitigation efforts have been proposed by STEP (\citealt{2006MNRAS.368.1323H, 2007MNRAS.376...13M}) and GREAT (\citealt{2010MNRAS.405.2044B, 2013ApJS..205...12K, 2015MNRAS.450.2963M}) challenges, to meet the requirements for the current imaging surveys. In particular, one of the state-of-the-art self-calibration methods, \textsc{metacalibration} (\citealt{2017arXiv170202600H, 2017ApJ...841...24S}) has been shown to be able to substantially reduce the significance of shear bias. It has been confirmed that shear can be calibrated with \textsc{metacalibration} at the few-percent level in DES (\citealt{2018MNRAS.481.1149Z, 2020arXiv201103408G}), without accounting for galaxy blending and detection. Tackling the issue of blending/detection is one key step forward for the DES Y6 analysis and preparatory Rubin LSST work with the shear-dependent detection and calibration technique (\textsc{metadetect}; \citealt{2020ApJ...902..138S}). While the major advantage of \textsc{metacalibration} is that it can be directly applied to real galaxy images without needing to rely on an ensemble calibration from image simulations, limitations for future surveys are not well-known.

One possible limitation might lie in the effect of undersampled images in space-based misssions like \emph{Euclid} and \emph{Roman}, which have such a small pixel scale that images will not be Nyquist sampled in the near-infrared at the detector pixel scale (\citealt{2013PASP..125.1496S}) based on the Nyquist-Shannon Sampling Theorem. We define the sampling factor of each filter in \emph{Roman} to be, 
\begin{equation}
    Q = \frac{\lambda_{min}N_{f}}{p}, 
    \label{eqn:sampling}
\end{equation}
where $\lambda_{min}$ is the shortest wavelength of the incident light in the filter, $N_{f}$ is the focal ratio of the telescope ($N_{f}=7.8$ for \emph{Roman}) and $p$ is the pixel spacing of the sensor ($p=10\mu m$ for \emph{Roman}). An image with sampling factor $Q < 2$ is not Nyquist sampled (i.e., undersampled). The PSF needs to be interpolated and estimated from well-sampled images to deconvolve and measure shapes with, because the \emph{Roman} PSF has a complex structure that cannot be captured in the original undersampled images. It is, therefore, necessary to build a robust strategy to reconstruct well-sampled images to estimate the PSF to allow unbiased shape measurement.
Recently, Kannawadi et al. (2021) addressed this potential issue of the limitations of \textsc{metacalibration} on undersampled images in \emph{Euclid} image simulations. They found that for the \emph{Euclid} mission the shear estimate is biased by about 1$\%$ (\citealt{2021MNRAS.502.4048K}). It is mentioned that their result could be extended to the \emph{Roman} mission due to similarities in the instruments and for \emph{Roman} they predicted the multiplicative bias was more than 1\%. They show that these effects can be mitigated using additional weighting kernels in the measurement.

In this work, we explore how \textsc{metacalibration} performs using coadd images at higher resolution, taking advantage of the dithering of images in the reference HLIS. We use an updated suite of image simulations specifically made for the \emph{Roman} reference HLIS mission. Our work is based on the image simulation suite for the \emph{Roman} Space Telescope developed by \citet{2021MNRAS.501.2044T}, where we render star and galaxy images using \texttt{GalSim}\footnote{\url{ https://github.com/GalSim-developers/GalSim}} (\citealt{2015A&C....10..121R}). We describe several important updates to the simulation capabilities and realism following \cite{2021MNRAS.501.2044T}. We also implement for the first time \textsc{metacalibration} using the simulated imaging, so that we can start to explore if the shear calibration goals of the HLIS for \emph{Roman} ($m=~3.2\times10^{-4}$) (\citealt{2018arXiv180403628D}) can be achieved with current \textsc{metacalibration} pipelines,\footnote{We limit the study to \textsc{metacalibration} for now, since we can extract unblended cutouts of objects in our simulations.} or will require substantial additional development. \par

@@

\section{Simulations}
\label{sec:sims}
The base of our image simulations of the \emph{Roman} Space Telescope is the \emph{Roman} simulation suite\footnote{\url{ https://github.com/matroxel/roman_imsim}} developed by \citet{2021MNRAS.501.2044T}, which renders realistic galaxy and star images on 18 Sensor-Chip Assemblies (SCAs) of a 2.5$\times$2.5 deg$^{2}$ patch of the sky following the observing strategy for the 5-year reference mission and Cycle7 instrument specifications\footnote{\url{https://roman.gsfc.nasa.gov/science/Roman_Reference_Information.html}}. We begin by creating a truth catalog using the simulated galaxy distribution from the Buzzard simulation (\citealt{2019arXiv190102401D}), a photometric galaxy catalog sampled from the CANDELS survey (e.g., \citealt{2019ApJ...877..117H}), and a Milky Way simulation (Galaxia; \citealt{2011ApJ...730....3S}) for star positions and magnitudes. Then, the following properties are applied to each galaxy:
\begin{itemize}
    \item positions (RA, Dec),
    \item flux within each \emph{Roman} filter (F184/H158/J129/Y106),
    \item intrinsic galaxy shapes and random orientations,
    \item flux ratios of de Vaucouleurs bulge, exponential disk, and star-forming knots, and
    \item artificial gravitational lensing shears.
\end{itemize} 
Within four identical realizations of the simulation, we use four sets of gravitational shears ($e_{1}$, $e_{2}$)=\{(+0.02, 0.00), (-0.02, 0.00), (0.00, +0.02), (0.00, -0.02)\}. This approach helps us to reduce shape and measurement noise when taking the difference in recovered shapes to compute the multiplicative bias (\citealt{2019A&A...621A...2P}).

The next step of the process is to create postage stamps and SCA images using \texttt{GalSim}. In this stage, the point-spread function (PSF) is convolved with the stamps. Here, the \emph{Roman} PSF is rendered using the \texttt{galsim.roman} module under \texttt{GalSim}, which has implemented \emph{Roman}-specific instrument properties such as the PSF and World Coordinate System (WCS) for a given telescope pointing, rotation angle, and SCA.

After we generate the object stamps across all the SCAs and pointings, we create Multi-Epoch Data Structure (MEDS) files in which each unique object dictionary contains information of all the exposures it appears in. These MEDS files are generated according to the Hierarchical Equal Area isoLatitude Pixelisation (HEALPix) of $n_{side}=512$. They contain all objects that are located in that region of the sky partitioned according HEALPixel. \textcolor{red}{add healpix reference} Once the objects are sorted in MEDS files, we pass these multiple exposures with the corresponding PSFs to \texttt{ngmix}\footnote{\url{ https://github.com/esheldon/ngmix}} to fit the galaxy shapes with the Gaussian mixture fitting method (\citealt{2014MNRAS.444L..25S}). This shape measurement process produces shape catalogs from which the shear calibration bias can be calculated with \textsc{metacalibration}.

\begin{figure}
	\includegraphics[width=\columnwidth]{figure1.pdf}
	\vspace*{-3mm}
    \caption{The rotation of the Roman PSF produced from the \texttt{galsim.roman} module. The position angle (PA) which determines the rotation of the focal plane is $0^{\circ}$ and $30^{\circ}$. The rotation of the PSF is particularly important when an object has multiple exposures. As more exposures are rotated relative to one another on the sky, the average impact of the PSF will be rounder. This will translate to a substantially less-elliptical coadd PSF.}
    \label{fig:psfrot}
\end{figure}

\begin{figure*}
	\includegraphics[width=\textwidth]{figure2.pdf}
	\vspace*{-10mm}
    \caption{The top row shows the first entry of the single epoch images and its coadded image, and the corresponding single-epoch and coadded oversampled PSF images for an object with low signal-to-noise ratio (S/N=9.69). The bottom row shows the same for an object with high signal-to-noise ratio (S/N=1552.97). \textcolor{red}{is snr in single-epoch or coadd?}}
    \label{fig:singlecoadd}
\end{figure*}

\subsection{Updates to Simulation Capabilities}
In order to accomplish the science goals, and build and test weak lensing calibration pipelines for in \emph{Roman}, we have continued to update the realism of our image simulations. We have implemented and made updates to the following parts of the simulation framework to be able to better test shear calibration using \textsc{metacalibration}. 
\begin{itemize}
    \setlength\itemsep{1em}
    \item \textbf{Saturation Cuts}:
    We have implemented a pixel saturation limit of 100,000 electrons. This value is an approximate pixel saturation level, but in the next generation of the simulations we will use a more accurate pixel saturation limit measured directly from the flight candidate detectors.

    \item \textbf{Rotation of the \emph{Roman} PSF on the sky}:
    In the study by \textcolor{red}{Troxel et al. (2021)}, the rotations of the \emph{Roman} PSF with respect to the telescope rotation were not properly applied by the \texttt{galsim.roman} module. Since a non-rotating PSF produces an artificial preferred direction, which can translate to galaxy shapes through errors in the process of deconvolvution, properly accounting for the averaging of the PSF orientation across exposures due to the survey dithering strategy is essential for a realistic shear calibration estimate. There has been an update in the \texttt{galsim.roman} module to correctly rotate the PSF given the WCS of the SCA in a given telescope pointing. Figure \ref{fig:psfrot} shows an example of how the PSF for one SCA changes with the rotation angle of the telescope.

    \item \textbf{Single-band and Multiband Coadds}: 
    We have used the postage stamp coadds (\texttt{psc}) algorithm\footnote{\url{https://github.com/esheldon/psc}} to create coadditions of single-epoch postage stamps of individual objects. Coadds are usually performed to enhance the signal-to-noise ratio (S/N) of an image and mitigate the impacts of measurement noise, while allowing for better sampling of the image if the overlapping images are dithered. However, it is challenging to create a robust, continuous coadd PSF model over an entire image. This is mitigated if we instead construct small, local coadds (at the size of an object postage stamp cutout in this work), which is a method also utilized in \textsc{metadetection}. If we take advantage of fitting an object in the coadd instead of fitting multiple images of each object in each filter, we can save a factor of approx. six in computing time, which is the average number of exposures from the reference survey. Additionally, coadding is one way to reduce the effect of the undersampling of the images since the coadd can be better sampled due to dithering. For these reasons, we explore utilizing a coadding scheme for the \emph{Roman} galaxies. The detailed overview of the coadd process in \texttt{psc} is described in in Sec. \ref{subsec:psc}.

    \item \textbf{\textsc{metacalibration} in \texttt{ngmix}}: We implemented the \textsc{metacalibration}\footnote{\url{https://github.com/esheldon/ngmix/wiki/Metacalibration}} bootstrapper method, which is a wrapper class to run measurements in the \texttt{ngmix} package and was used to produce the weak lensing shape catalog in the DES Y3 analysis \textcolor{red}{citation}. The \textsc{metacalibration} process can be performed on single-epoch or coadd images in each bandpass. With this calibration method, we hope to significantly reduce some of the shear calibration bias \textcolor{red}{Troxel et al. (2021)} measured in order to make comparisons of effects contributing to the bias more realistic and meaingful as we explore future \emph{Roman} pipeline development. The detailed overview of \textsc{metacalibration} can be found in Sec.\ref{subsec:mcal}. 
    %\item (Any other changes?)
\end{itemize}

@@

\section{Coadd and shear calibration pipelines}
\label{sec:methods}
Our goal is to test whether the recovered shapes with \textsc{metacalibration} are non-biased for \emph{Roman}. In order to do so, we need to build measurement pipelines within the current simulation framework that produces a final calibrated shear measurement. In this section, we present in detail how coadd images are produced with \texttt{psc} from the undersampled single-epoch images and how \textsc{metacalibration} is implemented to calibrates the measured shear using the \textsc{metacalibration} catalog.
